### 2018-12-10 paper/paper.tex
remove typo
Add sections on classifiers, tuning, and results
Also set margin to 1" and put in autoref

\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{sectsty}
\usepackage{multicol, caption}
\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage{subfig}
%\usepackage{subcaption}

%\usepackage{biblatex}
\usepackage[margin=0.5in]{geometry} % don't know what size margins to use
\newenvironment{Figure}
  {\par\medskip\noindent\minipage{\linewidth}}
  {\endminipage\par\medskip}

\setlength{\columnsep}{1cm}
%\addbibresource{paper.bib}
%\nocite{*}
\sectionfont{\fontsize{12}{15}\selectfont}

@@

            In this paper we explore the selection public datasets, data preparation,
            feature extraction and finally the selection and tuning of classifiers.
            We will do this following the process illustrated in Figure \ref{fig:process}.
        \section{Dataset Selection}
            The correct selection of a dataset was crucial to the testing of 
            different types of features. There were many characteristics that were
            on our `wishlist.' Such as having the freedom of processing 
            the raw text ourselves and determining what features may be important, 
            and not have the data preproccesed or turned into vectors.
            Next we wanted data that was conversational, that didn't use too much 
            slang or leetspeak and was in general proper English. The size of the
            dataset needed to be fairly large, at least 1000, for frequency analysis.
            Lastly, we would like a dataset that was referenced in multiple papers to make comparisons
            of our results to others.

@@

            With so much metadata given with this dataset, we wanted to take advantage
            of it for use as potential features. In preprocessing we found many features
            that could signature of spam emails such as excessive links or attachments.
            The processes illustrated with Figure \ref{fig:preprocess}, is an overview
            of the processes that will be preformed in this step.

@@

            \begin{minipage}{0.4\columnwidth}
                \includegraphics[width=\textwidth]{figures/spam_wc}
                \captionof{figure}{Spam}
                \label{spam_wc}
            \end{minipage}
            \begin{minipage}{0.4\columnwidth}
                \includegraphics[width=\textwidth]{figures/ham_wc}
                \captionof{figure}{Ham}
                \label{ham_wc}
             \end{minipage}
            This is more text
        %\section{Classifier Selection}

        %\section{Classifier Tuning}
            % Grid Search and Cross Validation
            % play with Max amount of features to see if have effect
        %\section{Results}
            % important metrics, why
        %\section{Evaluation}

>>>>

\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{sectsty}
\usepackage{multicol, caption}
\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage{subfig}
\usepackage{hyperref}
%\usepackage{subcaption}

%\usepackage{biblatex}
\usepackage[margin=1.0in]{geometry} % don't know what size margins to use
\newenvironment{Figure}
  {\par\medskip\noindent\minipage{\linewidth}}
  {\endminipage\par\medskip}

\setlength{\columnsep}{1cm}
%\addbibresource{paper.bib}
%\nocite{*}
\sectionfont{\fontsize{12}{15}\selectfont}
\subsectionfont{\fontsize{12}{15}\selectfont}

@@

            In this paper we explore the selection public datasets, data preparation,
            feature extraction and finally the selection and tuning of classifiers.
            We will do this following the process illustrated in \autoref{fig:process}.
        \section{Dataset Selection}
            The correct selection of a dataset was crucial to the testing of 
            different types of features. There were many characteristics that were
            on our `wishlist.' Such as having the freedom of processing 
            the raw text ourselves and determining what features may be important, 
            and not have the data preproccesed or turned into vectors.
            Next we wanted data that was conversational, that didn't use too much 
            slang or leetspeak and was in general proper English. The size of the
            dataset needed to be fairly large, at least 1000, for frequency analysis.
            Lastly, we would like a dataset that was referenced in multiple papers to make comparisons
            of our results to others.

@@

            With so much metadata given with this dataset, we wanted to take advantage
            of it for use as potential features. In preprocessing we found many features
            that could signature of spam emails such as excessive links or attachments.
            The processes illustrated with \autoref{fig:preprocess}, is an overview
            of the processes that will be preformed in this step.

@@

            \begin{minipage}{0.4\columnwidth}
                \includegraphics[width=\textwidth]{figures/spam_wc}
                \captionof{figure}{Spam}
                \label{spam_wc}
            \end{minipage}
            \begin{minipage}{0.4\columnwidth}
                \includegraphics[width=\textwidth]{figures/ham_wc}
                \captionof{figure}{Ham}
                \label{ham_wc}
             \end{minipage}
            This is more text

        \section{Classifier Selection}

            We selected various classifiers from the scikit-learn Python library. The 
            classifiers chosen for evaluation were Random Forest, K-Nearest Neighbors (KNN), 
            Support Vector Machine (SVM) with the radial basis function (RBF) kernel, and Bernoulli 
            Naive Bayes. All were chosen because they are well-known supervised machine learning 
            algorithms and generally good for classification tasks.

        \section{Classifier Tuning}
            Once the classifiers were selected, we tuned them using a grid search with 5-fold 
            cross-validation maximizing accuracy. The parameters evaluated for each classifier along 
            with the chosen classifier parameters are as follows:

            \noindent\textbf{Random Forest}
            \begin{itemize}
                \setlength\itemsep{0em}
                \item Number of Estimators: 40
                \item Maximum Tree Depth: 40
            \end{itemize}
            \textbf{K-Nearest Neighbors}
            \begin{itemize}
                \setlength\itemsep{0em}
                \item Number of Neighbors: 10
                \item Weight by Distance?: Yes
            \end{itemize}
            \textbf{SVM}
            \begin{itemize}
                \setlength\itemsep{0em}
                \item Error Penalty: 10
                \item RBF Kernel Coefficient: 0.001
            \end{itemize}
            \textbf{Bernoulli Naive Bayes}
            \begin{itemize}
                \setlength\itemsep{0em}
                \item Learn Prior Probabilities?: No
                \item Smoothing?: None
            \end{itemize}

            We also examined the effect of tuning the number of feature words chosen by the TF-IDF 
            extractor. The number of feature words chosen for initial analysis was 50, but subsequent 
            tests ranged from 50 to 1050 in steps of 200.
        \section{Results}
            Classifiers were evaluated on precision and recall on the spam class. Overall, precision is
            weighted more heavily than recall in the evaluation because it would likely be more disruptive 
            to classify a ham email as spam than to let a spam message slip through.
            \subsection{General Precision and Recall}
                Overall, the classifiers performed well with just features extracted from the email body.
                Precision and recall comparison can be found in \autoref{fig:precision_recall} with direct 
                number comparison in \autoref{tab:precision_recall}.

                \begin{Figure}
                    \begin{tabular}{|l|l|l|}
                    \hline
                                  & Precision & Recall \\ \hline
                    KNN           & 90.91     & 51.02  \\ \hline
                    Naive Bayes   & 83.67     & 83.67  \\ \hline
                    Random Forest & 98.84     & 86.73  \\ \hline
                    SVM           & 83.33     & 40.82  \\ \hline
                    \end{tabular}
                    \captionof{table}{Precison and Recall}
                    \label{tab:precision_recall}
                \end{Figure}

                \begin{Figure}
                    \centering
                    \includegraphics[width=\linewidth]{figures/precision_recall.png}
                    \captionof{figure}{Precison and Recall Comparison}
                    \label{fig:precision_recall}
                \end{Figure}

                While all classifiers had a precision greater than 80\%, the recall clearly divides the 
                classifiers into two groups. Those with over 80\% recall were Random Forest and Naive Bayes, 
                while the KNN and SVM both had a recall lower than 50\%.

                Overall, the Random Forest classifier performed the best under our evaluation criteria 
                with an almost perfect precision. In fact, only one ham instance was misclassified as spam. 
                Random Forest also performed best on recall. The Naive Bayes classifier performed second best 
                with an even recall and precision.

            \subsection{Effect of Number of Feature Words} 
                When increasing the number of feature words, precision increased dramatically for some classifiers. 
                Specifically, Naive Bayes and the SVM gained a precision increase of 10\% and 8\% respectively (See \autoref{fig:precision_word_effect}).
                However, the number of feature words did not seem to effect recall as much as precision (See \autoref{fig:recall_word_effect}).
                Only one classifier gained over 3\% precision from 50 feature words. Naive Bayes gained 10\% recall when increasing 
                the number of feature words from 50 to 250. This gain dropped off as the number of feature words increased.

                \begin{Figure}
                    \centering
                    \includegraphics[width=\linewidth]{figures/recall_wv_effect.png}
                    \captionof{figure}{Effect of the number of feature words on classifier recall}
                    \label{fig:recall_word_effect}
                \end{Figure}

                \begin{Figure}
                    \centering
                    \includegraphics[width=\linewidth]{figures/precision_wv_effect.png}
                    \captionof{figure}{Effect of the number of feature words on classifier precision}
                    \label{fig:precision_word_effect}
                \end{Figure}

                Interestingly, Naive Bayes dropped in precision by over 2\% 
                for 250 and 450 feature words before having the largest gain of any classifier. 
                Possibly, the gain in recall had a negative effect on the precision.
